Solutions to Integer Programming from Quantum Annealing

### 2020-05-28 paper/main.tex
Formatting

%----------------------------------------------------------------------------------------
\subsubsection{Integer linear programming}
\label{sec:methods:ilp-def}
%----------------------------------------------------------------------------------------
Formally, ILP is defined as the optimization of a linear function
\begin{align}
    \label{eq:initial-ip-def}
    \vec x_0 = \mathrm{arg} &\min\limits_{x}(\sum_i c_i x_i)
\end{align}
subject to
\begin{align}
    \label{eq:ilp-constraints}
    &\sum_i A_{ai}x_i +b_a \leq 0 \,,\\
    & x_i  \in \mathbbm{N}
\end{align}

@@

The inequality constraints in eq.~\eqref{eq:ilp-constraints} can be rewritten as an equality by introducing slack variables $s$ such that the ILP becomes
\begin{align}
    \vec x_0 = \mathrm{arg} &\min(\sum_i c_i x_i)\,,
\end{align}
subject to
\begin{align}& \sum_i A_{a i}x_i + s_a + b_a = 0,\\
    & s_a \in \mathbb{N},\\
    & x_i \in \mathbb{N}.
\end{align}
While the coefficients of the inequality constraints are not required to be integer valued, the inequalities can be trivially rescaled such that $s_i \in \mathbbm{N}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
As a result, we can restrict both $x_i$ and $s_i$ to sample over only positive integer values as allowed by Eq.~(\ref{eq:int_to_bin}).

@@

We map integer variables $\vec z = \vec x, \vec s$ to qubits under the following transformation~\cite{Chang:2018uoc}
\begin{align}
    z_i = & \sum_{r=0}^{R_i-1} 2^r \psi_{ri}
\label{eq:int_to_bin}
\end{align}
where $\psi_{ri} \in \{0, 1\}$.
The number of qubits used to represent the $i$-th integer variable is allowed to vary with $R_i$.
This transformation can be expressed as a rectangular matrix.
For example, a vector of two integer variables $z_0$ and $z_1$ represented by one and two qubits respectively is given as
\begin{align}
    \begin{pmatrix}
    z_0\\
    z_1
    \end{pmatrix}
    = &
    \begin{pmatrix}
    2^0 & 0 & 0\\
    0 & 2^0 & 2^1
    \end{pmatrix}
    \begin{pmatrix}
    \psi_{00}\\
    \psi_{01}\\
    \psi_{11}
    \end{pmatrix}
    \equiv T^z \begin{pmatrix}
    \psi_{00}\\
    \psi_{01}\\
    \psi_{11}
    \end{pmatrix}
\end{align}
If all variables are represented by the same number of qubits--$R_i$ is a constant for all $i$--then one can express the transformation as tensor product of bit vectors
\begin{align}
    \mathcal{R} = & \begin{pmatrix} 2^0 & \dots & 2^{R-1}\end{pmatrix},\\
    \mathcal{Z} = & \begin{pmatrix} z_0 & \dots & z_{N-1}\end{pmatrix},\\
    |\mathds{1}| = & |\mathcal{Z}|,\\
    T^z = & \mathds{1}\otimes \mathcal{R}.
\end{align}

@@

The integer quadratic optimization problem can be mapped to a minimization of the quadratic objective function
\begin{align}
    \chi^2 &= \left[\Psi^x_{\mu} T^x_{\mu i}d_{ij} T^x_{j \nu}\Psi^x_\nu + c_i T^x_{i\mu} \Psi^x_\mu \right.
    \nonumber\\ \label{eq:qubo-min}
    &\qquad\left.+ p (A_{a b} T^x_{b \mu} \Psi^x_{\mu} + T^s_{a \alpha} \Psi^s_\alpha + b_a)^2 \right],\\
    \vec x_0 &=  T^x \vec \Psi^x_0 \, ,
    \\
    (\vec \Psi^x_0, \vec \Psi^s_0) &= \mathrm{arg}\min\limits_{\vec{\Psi}}(\chi^2) \,, &
\end{align}
where $p$ is an external parameter representing the strength of the penalty when violating constraints.
The objective function can be represented as a QUBO Hamiltonian
\begin{align}
    E = &
    \begin{pmatrix}
    \Psi^x & \Psi^s
    \end{pmatrix}
    \begin{pmatrix}
    Q_{xx} & Q_{xs}\\
    Q_{sx} & Q_{ss}
    \end{pmatrix}
    \begin{pmatrix}
    \Psi^x\\ \Psi^s
    \end{pmatrix} + pb^2,\\
    \equiv & \Psi^T Q \Psi + C,
    \label{eq:matrix_form}
\end{align}
where
\begin{align}
    Q_{xx} = & {T^{x}}^T \left[ d + p A^T A + p \mathrm{Diag}_{x} \left(A^T b + b^T A\right) \right] T^x \nonumber \\
    &+ \mathrm{Diag}_{\psi^x}(c) T^x,\\
    Q_{xs} = & Q_{sx}^T = p {T^{x}}^T A^T T^s,\\
    Q_{ss} = & p\left[ {T^{s}}^T T^s + \mathrm{Diag}_{\psi^s}\left( {T^{s}}^T b + b^T T^s\right) \right].
\end{align}
The function $\mathrm{Diag}_{z}(v)$ embeds a vector $v$ into a diagonal matrix in subspace $z$, and absorbs the linear contributions of the QUBO into the diagonal elements of the quadratic representation.

@@

\begin{figure*}
    \centering
    \begin{tabular}{p{0.3\textwidth}p{0.3\textwidth}p{0.3\textwidth}}
    \includegraphics[width=0.20\textwidth]{./figures/subaru_ds.pdf}
    &
    \includegraphics[width=0.20\textwidth]{./figures/subaru_mds4.pdf}
    &
    \includegraphics[width=0.20\textwidth]{./figures/subaru_mds2.pdf}\\
    \centering\bf{a} & \centering\bf{b} & \centering\bf{c}
    \end{tabular}
    \caption{Example of different dominating sets for $G(V, E)$.
Vertices in the dominating set $D$ are highlighted in blue.
{\bf{a)}} A dominating set of $G$ with domination number $\overline{\overline{D}} = 5$.
{\bf{b)}} A minimal dominating set of $G$ with domination number of $\overline{\overline{D}} = 4$.
We note that $D$ is also the maximum independent set of $G$.
{\bf{c)}} The minimum dominating set of $G$ with domination number of $\overline{\overline{D}} = 2$.}
    \label{fig:dominating_sets}
\end{figure*}

For general graphs, existing "classical" algorithms either find minimal solutions in exponential time $\sim O( 1.5^n)$ \cite{Fomin2009, vanRooij2009} or approximate solutions in polynomial time.
For example, greedy algorithms locally optimize decisions about which nodes to add to the dominating set.
Thus one is guaranteed to find a dominating set but not necessarily a MDS.
We demonstrate an example greedy algorithm in figure Fig.~\ref{fig:mds-greedy}.
\begin{figure*}
    \centering
    \begin{tabular}{p{0.22\textwidth}p{0.22\textwidth}p{0.22\textwidth}p{0.22\textwidth}}
    \includegraphics[width=0.20\textwidth]{./figures/greedy-1.pdf}
&
    \includegraphics[width=0.20\textwidth]{./figures/greedy-2.pdf}
&
    \includegraphics[width=0.20\textwidth]{./figures/greedy-3.pdf}
&
    \includegraphics[width=0.20\textwidth]{./figures/greedy-4.pdf}\\
    \centering\bf{a} & \centering\bf{b} & \centering\bf{c} & \centering\bf{d}
    \end{tabular}
    \caption{
        Example of greedy MDS algorithm:
        The algorithm iteratively adds vertices to the dominating set (black nodes) such that newly added nodes are maximally unconnected (white nodes).
        Connected nodes are neighbors of the DS (turquoise) or already in the DS.
        In (a), one finds three maximally unconnected nodes [(2), (4), (7)] which are adjacent to three unconnected nodes each.
        In the first step $a\to b$, randomly the node (4) is picked.
        In (b), one has three unconnected choices [(1), (2)] with each adjacent to another unconnected node and one node [(6)] which is only adjacent to neighbors of the DS.
        After randomly selecting (2) when going from $b \to c$, only one unconnected node is remaining (6).
        The found solution is a (minimal) dominating set but not a MDS.
        To find the MDS using this greedy algorithm, the first node choice must be either (2) or (5).
    }
    \label{fig:mds-greedy}
\end{figure*}

@@

The solution to the minimum independent set can be expressed as an integer optimization problem given by,
\begin{align}
    f(x) = &\min\left(\sum_{\nu \in V} \psi^x_{\nu}\right),\\
    \textrm{subject to} \quad & \psi^x_{\nu} + \sum_{\mu \in \mathit{N}(\nu)} \psi^x_{\mu} \geq 1,\\
    & \psi^x_{\nu} \in \{0, 1\}
\end{align}
where the dimension of the dependent variable $x$ is the number of vertices $\overline{\overline{V}}$.
The problem minimizes the number of vertices in $D$ with a binary variable $\psi^x$ encoded by a single qubit, subject to the constraint that at least one vertex in $\mathit{N}(\nu)$ is in $D$.
For each vertex in $V$ we introduce slack variables $s_{\nu} = T^s_{\nu \alpha} \psi^s_{\alpha}$ to encode the inequality constraint such that
\begin{align}
    f(x) = &\min(\sum_{\nu\in V} \psi^x_{\nu}),\\
    \textrm{subject to} \quad & \psi^x_{\nu} + J_{\nu \mu} \psi^x_{\mu}- T^s_{\nu \alpha} \psi^s_{\alpha}  - 1 = 0,\\
    & \psi_{\nu} \in \{0, 1\},\\
    & 0 \leq s_{\nu} \leq |\mathrm{N}(\nu)|\\
    & s_{\nu} \in \mathbb{Z},
\end{align}
where the nearest-neighbor sum is expressed by $J$ (symmetric and zero diagonal), the adjacency matrix for $G$.
The algorithm uses $N_q = \overline{\overline{V}} + \sum_{\nu \in V} \log_2 \mathit(N(\nu))$ qubits---$\overline{\overline{V}}$ qubits to encode the vertices and another $\sum_{\nu \in V} \log_2 \mathit(N(\nu))$ qubits to embed the slack variables.
Therefore, the embedding at worse scales with $\overline{\overline{V}} \log_2 |\overline{\overline{V}}|$ qubits for fully connected graphs.

The target QUBO in the notation of eq.~\eqref{eq:matrix_form} reads
{\small
\begin{align}
    Q_{xx} &= \mathbbm{1} + p\left[J^T J + J^T + J - 2 \mathrm{Diag}_{\psi^x}(|J|) - \mathbbm{1} \right] \,,\\
    Q_{sx} &= - p(\mathbbm{1}+J^T)T^s\,,\\
    Q_{ss} &= p\left[{T^s}^T T^s + 2\mathrm{Diag}_{\psi^s}(|T^s|)\right]\,,\\
    C &=  p \overline{\overline{V}}\,,
\end{align}}
where $ |M| \equiv \sum_{\nu} M_{\nu \mu}$.

@@

To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
\begin{align}
    \partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
\end{align}
where $\rho (t)$ is the density matrix at time $t$.
$H(t)$ is the time-dependent Hamiltonian
\begin{align}
    \label{eq:annealH}
     H_{anneal}(t)&  =  - \sum_i  A_i(t)\sigma^x_i & \notag \\
     +&  \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i  ,&
\end{align}
where $A_i(t)$ and $B_{i}(t)$ are site-dependent annealing schedule functions.
The site dependency takes into account of the annealing offset.
$[,]$ denotes the Lie bracket.
$L_j$ are the Lindblad operators for decoherence.
$\{, \}$ denotes the anti-commutator.
In this study, we only include a minimal model for decoherence, i.e., the amplitude damping for non-interacting qubits.
The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where $\gamma = 1/T_1$ is the decoherence rate for relaxation time $T_1$.
For simplicity, we assume all qubits have the same relaxation time.
The initial condition is the Gibbs canonical ensemble
\begin{equation}
    \rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}[e^{-\beta H(0)}]} ,
\end{equation}
where $\beta$ is the inverse temperature.
The probability to obtain the ground state at for a single measurement is
\begin{align}
    P_{\mbox{gnd}} =  \mbox{Tr} \{  \rho (t) \pi_{\mbox{gnd}} \}  ,
\end{align}
where the projection operator onto the degenerated ground states subspace is defined as
\begin{equation}
	\pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i|
	\, .
\end{equation}
Here $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace, i.e., $\langle \mbox{gnd}_j | \mbox{gnd}_i \rangle = \delta_{ij}$.

@@

We demonstrate the proposed algorithm in order to obtain the MDS on a series of linear graphs $G(n)$ as shown in Fig.~\ref{fig:linear}.
This type of graph is chosen because the small number of nearest-neighbor connections is more efficiently embedded into the chimera graph allowing for scaling plots to be generated when using a DWave quantum annealer.
Additionally the MDS solution is known analytically, and contains both unique and degenerate solutions.
In particular, the domination number for $G(n)$ is $\lceil n/3 \rceil$ while the number of MDS solutions for $n$ vertices is
\begin{align}
    &1 &&\textrm{if} && n\textrm{ mod }3=0,\nonumber \\
    &2\lfloor n/3 \rfloor + 1 && \textrm{if}&& n\textrm{ mod }3=1,\nonumber \\
    &\lfloor n/3 \rfloor + 2 && \textrm{if} && n \textrm{ mod }3 = 2,
\end{align}
and gives the probability of randomly guessing the MDS of $G(n)$.

@@

>>>>

%----------------------------------------------------------------------------------------
\subsubsection{Integer linear programming}
\label{sec:methods:ilp-def}
%----------------------------------------------------------------------------------------
Formally, ILP is defined as the optimization of a linear function
\begin{align}
 \label{eq:initial-ip-def}
 \vec x_0 = \mathrm{arg} & \min\limits_{x}(\sum_i c_i x_i)
\end{align}
subject to
\begin{align}
 \label{eq:ilp-constraints}
  & \sum_i A_{ai}x_i +b_a \leq 0 \,, \\
  & x_i  \in \mathbbm{N}
\end{align}

@@

The inequality constraints in eq.~\eqref{eq:ilp-constraints} can be rewritten as an equality by introducing slack variables $s$ such that the ILP becomes
\begin{align}
 \vec x_0 = \mathrm{arg} & \min(\sum_i c_i x_i)\,,
\end{align}
subject to
\begin{align}              & \sum_i A_{a i}x_i + s_a + b_a = 0, \\
  & s_a \in \mathbb{N},                \\
  & x_i \in \mathbb{N}.
\end{align}
While the coefficients of the inequality constraints are not required to be integer valued, the inequalities can be trivially rescaled such that $s_i \in \mathbbm{N}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
As a result, we can restrict both $x_i$ and $s_i$ to sample over only positive integer values as allowed by Eq.~(\ref{eq:int_to_bin}).

@@

We map integer variables $\vec z = \vec x, \vec s$ to qubits under the following transformation~\cite{Chang:2018uoc}
\begin{align}
 z_i = & \sum_{r=0}^{R_i-1} 2^r \psi_{ri}
 \label{eq:int_to_bin}
\end{align}
where $\psi_{ri} \in \{0, 1\}$.
The number of qubits used to represent the $i$-th integer variable is allowed to vary with $R_i$.
This transformation can be expressed as a rectangular matrix.
For example, a vector of two integer variables $z_0$ and $z_1$ represented by one and two qubits respectively is given as
\begin{align}
 \begin{pmatrix}
  z_0 \\
  z_1
 \end{pmatrix}
 = &
 \begin{pmatrix}
  2^0 & 0   & 0   \\
  0   & 2^0 & 2^1
 \end{pmatrix}
 \begin{pmatrix}
  \psi_{00} \\
  \psi_{01} \\
  \psi_{11}
 \end{pmatrix}
 \equiv T^z \begin{pmatrix}
  \psi_{00} \\
  \psi_{01} \\
  \psi_{11}
 \end{pmatrix}
\end{align}
If all variables are represented by the same number of qubits--$R_i$ is a constant for all $i$--then one can express the transformation as tensor product of bit vectors
\begin{align}
 \mathcal{R} =  & \begin{pmatrix} 2^0 & \dots & 2^{R-1}\end{pmatrix},    \\
 \mathcal{Z} =  & \begin{pmatrix} z_0 & \dots & z_{N-1}\end{pmatrix},    \\
 |\mathds{1}| = & |\mathcal{Z}|,                 \\
 T^z =          & \mathds{1}\otimes \mathcal{R}.
\end{align}

@@

The integer quadratic optimization problem can be mapped to a minimization of the quadratic objective function
\begin{align}
 \chi^2                         & = \left[\Psi^x_{\mu} T^x_{\mu i}d_{ij} T^x_{j \nu}\Psi^x_\nu + c_i T^x_{i\mu} \Psi^x_\mu \right.
 \nonumber                                                                                                                             \\ \label{eq:qubo-min}
                                & \qquad\left.+ p (A_{a b} T^x_{b \mu} \Psi^x_{\mu} + T^s_{a \alpha} \Psi^s_\alpha + b_a)^2 \right],   \\
 \vec x_0                       & =  T^x \vec \Psi^x_0 \, ,
 \\
 (\vec \Psi^x_0, \vec \Psi^s_0) & = \mathrm{arg}\min\limits_{\vec{\Psi}}(\chi^2) \,,                                                 &
\end{align}
where $p$ is an external parameter representing the strength of the penalty when violating constraints.
The objective function can be represented as a QUBO Hamiltonian
\begin{align}
 E =    &
 \begin{pmatrix}
  \Psi^x & \Psi^s
 \end{pmatrix}
 \begin{pmatrix}
  Q_{xx} & Q_{xs} \\
  Q_{sx} & Q_{ss}
 \end{pmatrix}
 \begin{pmatrix}
  \Psi^x \\ \Psi^s
 \end{pmatrix} + pb^2, \\
 \equiv & \Psi^T Q \Psi + C,
 \label{eq:matrix_form}
\end{align}
where
\begin{align}
 Q_{xx} = & {T^{x}}^T \left[ d + p A^T A + p \mathrm{Diag}_{x} \left(A^T b + b^T A\right) \right] T^x \nonumber \\
          & + \mathrm{Diag}_{\psi^x}(c) T^x,                                                                    \\
 Q_{xs} = & Q_{sx}^T = p {T^{x}}^T A^T T^s,                                                                     \\
 Q_{ss} = & p\left[ {T^{s}}^T T^s + \mathrm{Diag}_{\psi^s}\left( {T^{s}}^T b + b^T T^s\right) \right].
\end{align}
The function $\mathrm{Diag}_{z}(v)$ embeds a vector $v$ into a diagonal matrix in subspace $z$, and absorbs the linear contributions of the QUBO into the diagonal elements of the quadratic representation.

@@

\begin{figure*}
 \centering
 \begin{tabular}{p{0.3\textwidth}p{0.3\textwidth}p{0.3\textwidth}}
  \includegraphics[width=0.20\textwidth]{./figures/subaru_ds.pdf}
                   &
  \includegraphics[width=0.20\textwidth]{./figures/subaru_mds4.pdf}
                   &
  \includegraphics[width=0.20\textwidth]{./figures/subaru_mds2.pdf} \\
  \centering\bf{a} & \centering\bf{b} & \centering\bf{c}
 \end{tabular}
 \caption{Example of different dominating sets for $G(V, E)$.
  Vertices in the dominating set $D$ are highlighted in blue.
   {\bf{a)}} A dominating set of $G$ with domination number $\overline{\overline{D}} = 5$.
   {\bf{b)}} A minimal dominating set of $G$ with domination number of $\overline{\overline{D}} = 4$.
  We note that $D$ is also the maximum independent set of $G$.
   {\bf{c)}} The minimum dominating set of $G$ with domination number of $\overline{\overline{D}} = 2$.}
 \label{fig:dominating_sets}
\end{figure*}

For general graphs, existing "classical" algorithms either find minimal solutions in exponential time $\sim O( 1.5^n)$ \cite{Fomin2009, vanRooij2009} or approximate solutions in polynomial time.
For example, greedy algorithms locally optimize decisions about which nodes to add to the dominating set.
Thus one is guaranteed to find a dominating set but not necessarily a MDS.
We demonstrate an example greedy algorithm in figure Fig.~\ref{fig:mds-greedy}.
\begin{figure*}
 \centering
 \begin{tabular}{p{0.22\textwidth}p{0.22\textwidth}p{0.22\textwidth}p{0.22\textwidth}}
  \includegraphics[width=0.20\textwidth]{./figures/greedy-1.pdf}
                   &
  \includegraphics[width=0.20\textwidth]{./figures/greedy-2.pdf}
                   &
  \includegraphics[width=0.20\textwidth]{./figures/greedy-3.pdf}
                   &
  \includegraphics[width=0.20\textwidth]{./figures/greedy-4.pdf}            \\
  \centering\bf{a} & \centering\bf{b} & \centering\bf{c} & \centering\bf{d}
 \end{tabular}
 \caption{
  Example of greedy MDS algorithm:
  The algorithm iteratively adds vertices to the dominating set (black nodes) such that newly added nodes are maximally unconnected (white nodes).
  Connected nodes are neighbors of the DS (turquoise) or already in the DS.
  In (a), one finds three maximally unconnected nodes [(2), (4), (7)] which are adjacent to three unconnected nodes each.
  In the first step $a\to b$, randomly the node (4) is picked.
  In (b), one has three unconnected choices [(1), (2)] with each adjacent to another unconnected node and one node [(6)] which is only adjacent to neighbors of the DS.
  After randomly selecting (2) when going from $b \to c$, only one unconnected node is remaining (6).
  The found solution is a (minimal) dominating set but not a MDS.
  To find the MDS using this greedy algorithm, the first node choice must be either (2) or (5).
 }
 \label{fig:mds-greedy}
\end{figure*}

@@

The solution to the minimum independent set can be expressed as an integer optimization problem given by,
\begin{align}
 f(x) =                    & \min\left(\sum_{\nu \in V} \psi^x_{\nu}\right),                    \\
 \textrm{subject to} \quad & \psi^x_{\nu} + \sum_{\mu \in \mathit{N}(\nu)} \psi^x_{\mu} \geq 1, \\
                           & \psi^x_{\nu} \in \{0, 1\}
\end{align}
where the dimension of the dependent variable $x$ is the number of vertices $\overline{\overline{V}}$.
The problem minimizes the number of vertices in $D$ with a binary variable $\psi^x$ encoded by a single qubit, subject to the constraint that at least one vertex in $\mathit{N}(\nu)$ is in $D$.
For each vertex in $V$ we introduce slack variables $s_{\nu} = T^s_{\nu \alpha} \psi^s_{\alpha}$ to encode the inequality constraint such that
\begin{align}
 f(x) =                    & \min(\sum_{\nu\in V} \psi^x_{\nu}),                                                 \\
 \textrm{subject to} \quad & \psi^x_{\nu} + J_{\nu \mu} \psi^x_{\mu}- T^s_{\nu \alpha} \psi^s_{\alpha}  - 1 = 0, \\
                           & \psi_{\nu} \in \{0, 1\},                                                            \\
                           & 0 \leq s_{\nu} \leq |\mathrm{N}(\nu)|                                               \\
                           & s_{\nu} \in \mathbb{Z},
\end{align}
where the nearest-neighbor sum is expressed by $J$ (symmetric and zero diagonal), the adjacency matrix for $G$.
The algorithm uses $N_q = \overline{\overline{V}} + \sum_{\nu \in V} \log_2 \mathit(N(\nu))$ qubits---$\overline{\overline{V}}$ qubits to encode the vertices and another $\sum_{\nu \in V} \log_2 \mathit(N(\nu))$ qubits to embed the slack variables.
Therefore, the embedding at worse scales with $\overline{\overline{V}} \log_2 |\overline{\overline{V}}|$ qubits for fully connected graphs.

The target QUBO in the notation of eq.~\eqref{eq:matrix_form} reads
 {\small
  \begin{align}
   Q_{xx} & = \mathbbm{1} + p\left[J^T J + J^T + J - 2 \mathrm{Diag}_{\psi^x}(|J|) - \mathbbm{1} \right] \,, \\
   Q_{sx} & = - p(\mathbbm{1}+J^T)T^s\,,                                                                     \\
   Q_{ss} & = p\left[{T^s}^T T^s + 2\mathrm{Diag}_{\psi^s}(|T^s|)\right]\,,                                  \\
   C      & =  p \overline{\overline{V}}\,,
  \end{align}}
where $ |M| \equiv \sum_{\nu} M_{\nu \mu}$.

@@

To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
\begin{align}
 \partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
\end{align}
where $\rho (t)$ is the density matrix at time $t$.
$H(t)$ is the time-dependent Hamiltonian
\begin{align}
 \label{eq:annealH}
 H_{anneal}(t) & =  - \sum_i  A_i(t)\sigma^x_i                                                                      & \notag \\
 +             & \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i  , &
\end{align}
where $A_i(t)$ and $B_{i}(t)$ are site-dependent annealing schedule functions.
The site dependency takes into account of the annealing offset.
$[,]$ denotes the Lie bracket.
$L_j$ are the Lindblad operators for decoherence.
$\{, \}$ denotes the anti-commutator.
In this study, we only include a minimal model for decoherence, i.e., the amplitude damping for non-interacting qubits.
The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where $\gamma = 1/T_1$ is the decoherence rate for relaxation time $T_1$.
For simplicity, we assume all qubits have the same relaxation time.
The initial condition is the Gibbs canonical ensemble
\begin{equation}
 \rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}[e^{-\beta H(0)}]} ,
\end{equation}
where $\beta$ is the inverse temperature.
The probability to obtain the ground state at for a single measurement is
\begin{align}
 P_{\mbox{gnd}} =  \mbox{Tr} \{  \rho (t) \pi_{\mbox{gnd}} \}  ,
\end{align}
where the projection operator onto the degenerated ground states subspace is defined as
\begin{equation}
 \pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i|
 \, .
\end{equation}
Here $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace, i.e., $\langle \mbox{gnd}_j | \mbox{gnd}_i \rangle = \delta_{ij}$.

@@

We demonstrate the proposed algorithm in order to obtain the MDS on a series of linear graphs $G(n)$ as shown in Fig.~\ref{fig:linear}.
This type of graph is chosen because the small number of nearest-neighbor connections is more efficiently embedded into the chimera graph allowing for scaling plots to be generated when using a DWave quantum annealer.
Additionally the MDS solution is known analytically, and contains both unique and degenerate solutions.
In particular, the domination number for $G(n)$ is $\lceil n/3 \rceil$ while the number of MDS solutions for $n$ vertices is
\begin{align}
  & 1                        &  & \textrm{if} &  & n\textrm{ mod }3=0,\nonumber \\
  & 2\lfloor n/3 \rfloor + 1 &  & \textrm{if} &  & n\textrm{ mod }3=1,\nonumber \\
  & \lfloor n/3 \rfloor + 2  &  & \textrm{if} &  & n \textrm{ mod }3 = 2,
\end{align}
and gives the probability of randomly guessing the MDS of $G(n)$.

@@

cpan -i File::HomeDir Unicode::GCString
